Predicting Success of Motivational Interviews with Recurrent Neural Network and Probabilistic Model for Patient-Provider Communication Sequences

### 2017-08-31 paper-amia-summit-2018/amia_summit_2018.tex
added figure for proposed rnn model

\section*{Results}
Experimental evaluation of the proposed method is conducted on both under- and over-sampled sequences.

@@

\subsection*{\textit{Predictive performance for over-sampled PPC code sequences}}
Table~\ref{tab:result_over_sampled} summarizes predictive performance of the proposed methods on alternating sequences. These results indicate that second-order HMM had better recall than MC, achieving 97.13\% recall. Similar to the case of natural sequences, prediction method based on second-order HMM has the highest recall of 0.9713 among all models. However, different from natural sequences, second-order MC has the highest precision (0.9778) as well as the highest F-measure (0.9736). We also observed that second-order MC and HMM outperform first-order MC and HMM. Specifically, moving from first-order to second-order MC improves precision, recall and F-measure of the MI success prediction method by 0.01\%, 2.72\% and 1.37\%, respectively. Moving from first-order to second-order HMM improves precision, recall and F-measure of the MI success prediction method by 3.32\%, 4.30\% and 3.70\%, respectively.\\

@@

>>>>

\section*{Results}
Experimental evaluation of the proposed method is conducted on both under- and over-sampled sequences. \\

@@

@@

\subsection*{\textit{Predictive performance for over-sampled PPC code sequences}}
Table~\ref{tab:result_over_sampled} summarizes predictive performance of the proposed methods on alternating sequences. These results indicate that second-order HMM had better recall than MC, achieving 97.13\% recall. Similar to the case of natural sequences, prediction method based on second-order HMM has the highest recall of 0.9713 among all models. However, different from natural sequences, second-order MC has the highest precision (0.9778) as well as the highest F-measure (0.9736). We also observed that second-order MC and HMM outperform first-order MC and HMM. Specifically, moving from first-order to second-order MC improves precision, recall and F-measure of the MI success prediction method by 0.01\%, 2.72\% and 1.37\%, respectively. Moving from first-order to second-order HMM improves precision, recall and F-measure of the MI success prediction method by 3.32\%, 4.30\% and 3.70\%, respectively.
